\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage[margin=0.65in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{xcolor}
\input{glyphtounicode}

\pagestyle{empty}
\urlstyle{same}
\raggedright
\raggedbottom
\setlength{\tabcolsep}{0in}
\pdfgentounicode=1

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\newcommand{\resumeItem}[1]{
  \item \small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in, itemsep=2pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

\begin{document}

\begin{center}
    {\LARGE \textbf{Chenfeng Huang}} \\[4pt]
    \href{mailto:chenfenghuang@ucla.edu}{chenfenghuang@ucla.edu}
    \,|\, \href{https://chenfenghuang.info}{chenfenghuang.info}
    \,|\, \href{https://github.com/chenfeng-huang}{github.com/chenfeng-huang}
    \,|\, \href{https://scholar.google.com/citations?user=F4u6rDoAAAAJ}{Google Scholar}
\end{center}

\section{Research Interests}
\small{
Interpretable machine learning, time series analysis, PAC-Bayesian learning, out-of-distribution generalization, and causal machine learning.
}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of California, Los Angeles}{Los Angeles, CA}
    {Ph.D. in Statistics}{2026 -- Present}
  \resumeItemListStart
    \resumeItem{Advisor: George Michailidis}
  \resumeItemListEnd

  \resumeSubheading
    {University of Southern California}{Los Angeles, CA}
    {M.S. in Applied Data Science}{2023 -- 2025}
  \resumeItemListStart
    \resumeItem{GPA: 4.0/4.0}
  \resumeItemListEnd

  \resumeSubheading
    {Santa Clara University}{Santa Clara, CA}
    {B.S. in Computer Science}{2020 -- 2022}
  \resumeItemListStart
    \resumeItem{GPA: 3.5/4.0}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Research Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Research Assistant}{Los Angeles, CA}
    {University of California, Los Angeles}{2026 -- Present}
  \resumeItemListStart
    \resumeItem{Developing a model-agnostic online PAC-Bayesian calibration framework for time series forecasting under distribution shift, combining martingale certificates with gated residual Bayesian correction to improve stability under covariate and concept shift.}
    \resumeItem{Investigating few-shot identification of linear dynamical systems through PAC-Bayesian meta-learning, deriving generalization guarantees under sequential dependence and enabling Bayesian adaptation from short, noisy trajectories.}
  \resumeItemListEnd

  \resumeSubheading
    {Research Assistant}{Raleigh, NC}
    {North Carolina State University}{2024 -- Present}
  \resumeItemListStart
    \resumeItem{Proposed an expert-guided causal Bayesian optimization framework with adaptive expert weighting, confidence-based handover, and safety checks to improve intervention quality in complex causal environments.}
    \resumeItem{Developed a causal jump-diffusion method for time-series anomaly detection that models latent environment shifts and contrasts factual and counterfactual trajectories for robust detection.}
    \resumeItem{Contributed to ongoing work on causal Bayesian optimization foundations and PAC-Bayesian methods for time-series generalization under dependence and distribution shift.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Selected Publications}
\begin{itemize}[leftmargin=0.15in, itemsep=4pt, topsep=2pt]
  \item \small{\textbf{C. Huang}, Z. Ma, and G. Michailidis. ``Model-Agnostic Online Certificate-Driven Calibration for Time Series Forecasting Under Distribution Shift.'' Under review, 2026.}
  \item \small{\textbf{C. Huang} and G. Michailidis. ``PAC-Bayesian Meta-Learning for Few-Shot Identification of Linear Dynamical Systems.'' Under review, 2026.}
  \item \small{Z. Ma, \textbf{C. Huang}, T. T. Le, and H. Tran. ``Confidence-Based Handover for Causal Bayesian Optimization with Adaptive Expert Trust.'' Under review, 2026.}
  \item \small{Z. Ma and \textbf{C. Huang}. ``A Causal Perspective on Jump-Diffusion for Time-Series Anomaly Detection.'' Under review, 2026.}
  \item \small{Z. Ma and \textbf{C. Huang}. ``Effective Series Decomposition and Components Learning for Time Series Generation.'' \emph{IEEE International Conference on Data Mining (ICDM)}, 2025.}
\end{itemize}

\section{Presentations}
\begin{itemize}[leftmargin=0.15in, itemsep=4pt, topsep=2pt]
  \item \small{\textbf{Joint Mathematics Meetings (JMM)}, 2026. ``Expert-guided Causal Bayesian Optimization.'' Abstract accepted for presentation.}
  \item \small{\textbf{IEEE International Conference on Data Mining (ICDM)}, 2025. ``Effective Series Decomposition and Components Learning for Time Series Generation.''}
\end{itemize}

\section{Teaching Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Mathematics Tutor}{Rocklin, CA}
    {Sierra College}{2018}
  \resumeItemListStart
    \resumeItem{Tutored Calculus I and Calculus II students in one-on-one and small-group settings.}
    \resumeItem{Completed the College Reading and Learning Association (CRLA) Level I tutor training program.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Selected Honors}
\begin{itemize}[leftmargin=0.15in, itemsep=4pt, topsep=2pt]
  \item \small{Kaggle Silver Medal, \emph{Detect Behavior with Sensor Data}, rank 16/2657 (top 1\%), 2025.}
  \item \small{Kaggle Silver Medal, \emph{Charting Student Math Misunderstandings}, rank 92/1858 (top 5\%), 2025.}
  \item \small{Kaggle Silver Medal, \emph{Child Mind Institute Problematic Internet Use}, rank 111/3599 (top 3\%), 2024.}
\end{itemize}

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, itemsep=2pt, topsep=2pt]
  \item \small{\textbf{Languages:} Python, C/C++, Java, SQL}
  \item \small{\textbf{Machine Learning and Data:} PyTorch, TensorFlow, MLflow, Hadoop, MongoDB}
  \item \small{\textbf{Tools:} Linux, Git}
\end{itemize}

\end{document}
